\textbf{Optimization of Porous Silicon Gradient Refractive Index Structures.}

### 2020-06-17 paper.tex

We assume that our electrolytic cell has the shape of a
prism (see Fig. \ref{f:celda}) with a horizontal rectangular base of sides $a$ and $b$, and
filled with the electrolyte up to a height $c$. We assume that the
walls of the cell are insulating while the bottom is completely
covered with the sample, which is a which is an
electrically grounded good conductor. Within the electrolyte we position an electrode
which we assume is a thin conductor, insulated from the electrolyte
but for a small area near its tip, which we thus approximate as a
point current source.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{Images/celdan1}
  \caption{Prism shaped electrolytic cell with a rectangular base of
    sides $a$, $b$ filled with electrolyte up to a height $c$. The
    walls of the cell are insulating and the bottom is completely
    covered by the sample, which is assumed to be a good
    conductor. The tip of the electrode is a thin insulated wire
    \notaL{El punto del electrodo hazlo más chico que el ancho
      del cable.} with just the tip uncovered and located at $\bm r_0=(x_0,y_0,z_0)$ within the
    liquid.}
  \label{f:celda}
\end{figure}
Within the electrolyte the current density is
\begin{equation}
  \label{eq:j}
  \bm j=\sigma\bm E,
\end{equation}
with
$\sigma$ the conductivity, $\bm E=-\nabla\varphi$ the electric field,
and $\varphi$ the electric potential. For a
stationary situation\notaL{Latex usa nabla como el nombre de
  $\nabla$}
$\nabla\cdot \bm j = \sigma\nabla\cdot\bm E=0$. Thus, within the electrolyte,
\begin{equation}
  \label{eq:laplace}
\nabla^{2} \varphi=0.
\end{equation}
Consider now an arbitrary closed surface
$\mathcal S$
within the electrolyte that surrounds completely the tip of the
electrode. Integrating $ \bm j$ over this surface we obtain
\begin{equation}
  \label{eq:I}
\int_{\mathcal S'} d\bm a \cdot \bm j = -I,
\end{equation}
where the prime on $\mathcal S'$ means we remove from the surface a
very small hole through which the wire that feeds the current to the
electrode gets
through. Assuming the wire is narrower than any other relevant
distance in the system, we may interpret Eq. \eqref{eq:I} as an
integral over a closed surface of the current \eqref{eq:j} within the
electrolyte, ignoring the actual current within the wire. Thus
\begin{equation}
  \label{eq:gauss}
  \int_{\mathcal S} d\bm a \cdot \bm E = -\frac{I}{\sigma}
\end{equation}
Using Gauss's law, we interpret this equation as a source for the
potential in the form of a point charge
\begin{equation}
  q_0 = -\frac{I}{4 \pi \sigma}
\end{equation}
at the position $\bm r_0=(x_0, y_0, z_0)$ of the
tip of the electrode. Note that $q_0$ would be the total charge,
and it shouldn't be further screened through the permittivity of the
electrolyte.

@@

We consider first a system made of identical unit charges
ocuppying the positions $\bm R$ of a 2D Bravais lattice $\{\bm R\}$,
which we will take as a rectangular lattice with lattice parameters
$2a$ and $2b$, and lying, for the time being, at the $z=0$ plane.
The potential it produces obeys
\begin{equation}
  \label{eq:poissonRed}
  \nabla^2\varphi(\bm r)=-4\pi\sum_{\bm R}\delta(\bm r_\|-\bm
  R)\delta(z)=-\frac{4\pi}{A}\sum_{\bm G}e^{i\bm G\cdot\bm r_\|}\delta(z),
\end{equation}
where $\bm r_\|$ is the projection of the observation position $\bm
r=(x,y,z)$ onto the $xy$ plane,
$\delta(\ldots)$ is Dirac's delta function, $\{\bm G\}$ is the
reciprocal lattice defined through $e^{i\bm G\cdot\bm R}=1$ for all
$\bm R$ and $\bm G$, $A=4ab$ is the area of the unit cell
and we used the Fourier representation of the 2D
periodically repeated delta function. We introduce a 2D Fourier representation for
the potential \notaL{Checar consistencia entre phi y varphi en todos lados}
\begin{equation}
  \label{eq:phifourier}
  \phi(\bm r)=\sum_{\bm G}\phi_{\bm G}(z)e^{i\bm G\cdot\bm r_\|}
\end{equation}
where $\phi_{\bm G}(z)$ is the Fourier coefficient of the potential at
the height $z$. Substitution in Eq. \eqref{eq:poissonRed} yields the
ordinary differential equation \notaL{El signo estaba mal. Chécalo.}
 \begin{eqnarray}
 \frac{d^2}{dz^2}\phi_{\bm G}(z)-G^2\phi_G(z)=
   -\frac{4 \pi}{A} \delta(z),
 \end{eqnarray}
an homogeneous equation for $z\ne0$ which may be trivially
solved. After applying boundary conditions at $z=0$ and regularity
conditions at infinity, we obtain
\begin{equation}
  \label{eq:phiG}
  \phi_{\bm G}(z)=
  \begin{cases}
    -\dfrac{2\pi}{A}\abs{z}&\text{if }G=0,\\
    \dfrac{2 \pi}{AG}  e^{- G \abs{z}}&\text{if }G\neq 0.
  \end{cases}
\end{equation}
The case $G=0$ corresponds to the potential produced by a uniformly charged plane,
while the case $G\ne 0$ is the potential produced by a sinusoidal
charge density on a plane given by the
symmetric solution that decays exponentially as we get away from
the source plane. Substituting into Eq. \eqref{eq:phifourier} yields
\begin{eqnarray}
  \label{eq:phiG1}
 \phi(\bm r) = -\frac{2 \pi}{A}  \abs{z} +{\sum_{\bm G}}' \frac{2 \pi
   }{AG} e^{- G \abs{z}} e^{i \bm G\cdot\bm r_\|},
 \end{eqnarray}
where the prime indicates that the term $G=0$ should be ommited from
the sum.

@@

\notaL{Cambié el título, pues tienes una mezcla de experimento y
  teoría aquí}
In Fig. \ref{fig:DE1} we show a schematic representation of our
experimental setup to manufacture porous silicon with GRIN.
\notaL{Cambié las figuras}
As dicussed above, we fabricated an electrolytic cell with the shape of a
rectangular prism on the bottom of which we place a Si wafer which makes
electrical contact to a gold plate \notaL{Lo inventé; de qué material es
  el contacto bajo la muestra} which together make the anode. The
catode consists of a platinum wire insulated except for a small region
at its tip, which we take as a point current drain.
We also show a schematic drawing of the expected GRIN PS structures,
with a gradient in the porosity, and in the thickness, density and depth
of the resulting pores.

\subsection{Fabrication of PS  GRIN Single Layers}
\label{sec:fabrication-ps-grin}
We manufactured single layer PS structures through an electrochemical
anodization on a (100) $p$-type crystalline Si wafer
(resistivity 0.002 - 0.005 $ \Omega\,\text{cm}$), under galvanostatic
conditions. The process was performed at
room temperature,\notaL{OJO. No controlaste la temperatura} with an
electrolytic mixture of aqueous hydrofluoric
acid (HF) (concentration 48\% wt), glycerol (purity 99.8 \% wt) and
ethanol (purity 99.9\% wt) in a 3:7:1 volume ratio. After the
anodizing process, the samples were rinsed with
ethanol (purity: 99.9 $ \% $  wt). The electrolytic cell had the shape
of a rectangular prism as shown in Fig. \ref{fig:DE1}, with a base of
size $6.2\text{mm}\times2.03\text{cm}$) with an uncovered sample area
of about $1.21\text{cm}^2$. The height of the liquid was set at
$c=1\text{cm}$. The cathode was a
platinum wire that with a diameter of $0.41\text{mm}$ insulated by a
teflon cylinder of external diameter $2\text{mm}$. \notaL{¿Están
  bien estos diámetros?} with an uncovered tip located at $\bm r_0=(x_0,
y_0,z_0)=(0.1,0.31,0.9)$.
\notaL{Cambiar figura a una adecuada}
We manufactured samples using a current $I=5\text{mA}$
which yielded current densities in the range
$j_\perp=2.5-6.0\text{mA}/\text{cm}^2$ and other samples using a larger
current $I=40\text{mA}$ corresponding to current densities in the
range $j_\perp=20-50\text{mA}/\text{cm}^2$.
\subsection{Morphological studies}
\label{sec:morph-stud}
\notaL{Cambié el orden}
The morphologies of the etched porous layers were
observed using a Hitachi SU1510 scanning electron microscope (SEM)
with which we measured the thickness $d$ and the porosity $p$ of the
films at different positions along the sample from its top and side
views (Fig. \ref{fig:DE1}).

\subsection{Reflectance Measurement}
\label{sec:refl-meas}
We measured the reflectivity spectra using a {\em Perkin Elmer Lambda 950}
UV-Vis-NIR spectrophotometer. For iterpretation of the data in the
case of a single PS layer we used
the standard formula \notaL{referencia} for three media air (0), PS
(1) and c-Si (2),
 \begin{eqnarray}\label{Eq:ECMR}
   R=\frac{r _ {_ {01}}r _ {_ {12}} e^{2i\delta}}{1+r _ {_ {01}}r _ {_ {12}} e^{2i\delta}}
\end{eqnarray}
where $ r_{01} $ y $ r_{12}$ are the Fresnel reflectance
coefficients at the air/PS and PS/c-Si interfaces \notaL{referencias}
and $\delta=k_{PS}^\perp d$, where $k_{PS}^\perp$ is
the component of the wavevector perpendicular to the surface within
the porous layer of thickness $d$.
\notaL{Me tienes que explicar dónde y cómo usaste lo que mencionas en
  la siguiente frase:
The advantage of this method is
the possibility of taking into account the interface roughness effect
by including the Davies-Bennett factor in the coefficient of each
Fresnel \cite{I17, I18, I19}, which represents the roughness of a
Gaussian distribution.}

\subsection{Refraction Index of PS GRIN Single Layers}
\label{sec:refraction-index-ps}
The local refractive index $n_{PS}$ of the PS layer was calculated from its
porosity $p$ through
Bruggeman's effective medium theory \cite{I20} \notaL{Elegir y checar:
  varepsilon o epsilon para funciones dieléctricas}
\begin{eqnarray}\label{Eq:Brugg}
 p\frac{1-\varepsilon_{PS}} {1+\varepsilon_{PS}} + (1-p)
  \frac{\varepsilon_{\text{Si}} - \varepsilon_{PS}}
  {\varepsilon_{\text{Si}}+\varepsilon_{PS}}=0
\end{eqnarray}
\notaL{Te faltaba la igualdad}
where the porosity $p$ is the volume fraction of air within the PS
layer, $\varepsilon_{Si}$ is the dielectric function of c-Si, and
$\varepsilon_{PS}=n_{PS}^2$ is the dielectric function of the PS.
\notaL{Quité frases irrelevantes.}
\subsection{Fabrication  of GRIN PS Microcavities}
\label{sec:fabrication-grin-ps}
After characterizing the fabrication process through measurements and
calculations corresponding to single PS GRIN layers, we
fabricated PS GRIN microcavities (MC) as specific defects between two distributed Bragg
mirrors  (DBR). Alternate quarter wavelength plates of high (H) and low (L)
refractive indices $n_i$ of thickness $d_i$, $i=H,L$ were prepared satisfying the Bragg condition
$n_id_i=\lambda_c/4$ at a given design
wavelength $\lambda_c$ and at a position $A$ (Fig. \ref{fig:DE1}) which
we chose as that directly below the point-like electrode.\notaL{Checar
  veracidad} The defect
was chosen as a half-wavelength high index layer of thickness $d_d=2d_H$ such that
$n_Hd_d=\lambda_c/2$. The MC corresponds to the
sequence $(HL)_6HH(LH )_6$ where each letter $H$ or $L$ corresponds to
a quarter wavelength plate of high and low index of refraction correspondingly.
We chose $\lambda_c= 0.67 \mu\text{m}$.\notaL{Algún motivo para esta
  elección?} For preparing the high index layers we
chose a current $I_H=5\text{mA}$ which corresponded to a current density
$j_{HA\perp}= 6\text{mA}/\text{cm}^2$ below the tip \notaL{checar}, and yielded
$n_H =2.6$, corresponding to a porosity \notaL{Explicar esta
  correspondencia entre $p$ y $n$} \notaL{P mayúscula
  es porosidad, o p minúscula. Checar consistencia} $p_H =0.46$, and a
thickness $d_H=0.066 \mu\text{m}$, which required an attack time of
$t_H=35 \text{s}$. The corresponding parameters for the low density
layers were $I_L=38\text{mA}$, $j_{LA\perp}=50\text{mA}/\text{cm}^2$, $n_L= 1.4$,  $P_L =0.75$,
$d_L=0.117 \mu \text{m}$, and $t_L=11 \text{s}$. For the rest of the
sample the current density, porosity, index of refraction and thickness
varied, yielding a GRIN MC.

@@

\subsection{PS GRIN Single Layer }
\label{sec:ps-grin-single}
\notaL{Quité la figura pues no añade nada}
\notaL{Quité la descripción, pues está arriba}
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{Images/SPgrin51}
  \caption{(a)  Sample $G_1$ prepared as described in
     \ref{sec:fabrication-ps-grin} using a current $I_1=5 \text{mA}$
    during a time $t_1=600\text{s}$. We indicate three regions $A$,
    $B$, and $C$ centered at positions at positions,
    $x_A=0.3\text{cm}$ \notaL{Atrás habías dicho que era justo abajo
      del electrodo. ¿Es cierto o no? ¿Dónde estaba el electrodo? ¿Qué
    altura tenía el agua? ¿Igual que en la sección previa?}, $x_B=0.8\text{cm}$ and
    $x_C=1.7\text{cm}$. \notaL{¿Cuánto vale $y$?} (b) Reflectance
    spectra measured at the center of regions $A$, $B$, and $C$ and fit
    using Eq. \eqref{Eq:ECMR}.\notaL{¿Cuáles parámetros se ajustaron y
      cuáles se midieron independientemente}\notaL{Para que no se vean
      tan chicas las figuras, quita las R's y los números en el segundo
      renglon, excepto en el extremo izquierdo, y pega las tres
      figuras una tras la otra. Haz lo mismo en el tercer renglón,
      quitando dos de los letreros Refractive index, pero antes
      asegúrate de usar la misma escala en las tres figuras} (c)
    Corresponding complex indices of refraction $n+ik$ obtained from
    Eq. \eqref{Eq:Brugg} using the fitted porosities $p_{1A}=0.44$,
    $p_{1B}=0.42$, and $p_{1C}= 0.40$ at the chosen positions. \notaL{En las
      figuras escribe A, B y C en lugar de
      Point A, Point B y Point C. Escribe $p_{1A}$, $p_{1B}$ y $p_{1C}$ en lugar
      de la palabra Porosity. Escribe $n$ y $k$ nada más, sin la
      palabra Real ni Imaginary. Usa Theory en lugar de
      Simulation. Usa línea a trazos para la parte
      imaginaria. Alínea todos los letreros. En inglés, los rótulos
      a), b) y c) se escriben como (a), (b) y (c), aunque creo que se
      pueden eliminar (porque además, no los alineaste bien). }
  \notaL{A ojo no se notan las diferencias en epsilon. Mejor junta las
  tres partes reales en una sola gráfica y las tres partes imaginarias
en otra y ponerlas una al lado de la otra.}\notaL{Las letras A, B y C
están colocadas en el lugar preciso, a escala?}\notaL{Quizás sea mejor
que hagas tres figuras distintas, una para cada panel, y las alineamos
con latex}}
  \label{fig:DR3}
\end{figure}
 In Fig. \ref{fig:DR3} we show a photograph of one of our single layer PS GRIN
 structures, $G_1$, prepared as described in
 \ref{sec:fabrication-ps-grin} applying a current $I_1=5\text{mA}$ for
 $t_1=600\text{s}$.\notaL{Quizás podamos quitar la repetición de I y
   t} We employed the same geometry as that described in
 Sec. \ref{sec:current-density} \notaL{Lo inventé. ¿Es cierto?}
The position of electrode corresponds to the upper left side of the
photograph. The variation of the optical properties across the
sample is evident. We chose three positions $x_A=0.3\text{cm}$,
$x_B=0.8\text{cm}$ and $x_C=1.7\text{cm}$ \notaL{¿Son correctos estos
  valores? Antes dijiste que $A$ estaba abajo del electrodo}\notaL{¿valor de y?} on
which we measured the reflectance spectra, also shown in the figure.
We fitted the measurements using Eqs. \eqref{Eq:ECMR} and
\eqref{Eq:Brugg} using the local porosity and the depth of the layer
as adjustable parameters. \notal{¿Es cierto?} We obtained $p_{1A}=0.44$, $p_{1B}=0.42$, and
$p_{1C}= 0.40$. \notaL{Falta decir cuáles fueron las profundidades}
Location $A$ is
closest to the electrode, while location $C$ is the furthest.
\notaL{Quité una frase sin sentido.}
We also show in Fig. \ref{fig:DR3} the wavelength dependence of
 the complex index of refraction corresponding to the fitted porosities.
\notaL{Quité otra frase que no entendí, pero que me generó una duda:
  la profundidad la ajustaste ópticamente o la mediste en SEM y luego
  hiciste el ajuste a la reflectancia?}

@@

>>>>

We assume that our electrolytic cell has the shape of a
prism (see Fig. \ref{f:celda}) with a horizontal rectangular base of sides $a$ and $b$, and
filled with the electrolyte up to a height $c$. We assume that the
walls of the cell are insulating while the bottom is completely
covered with the sample, which is a which is an
electrically grounded good conductor. Within the electrolyte we position an electrode
which we assume is a thin conductor, insulated from the electrolyte
but for a small area near its tip, which we thus approximate as a
point current source.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{Images/celdan1}
  \caption{Prism shaped electrolytic cell with a rectangular base of
    sides $a$, $b$ filled with electrolyte up to a height $c$. The
    walls of the cell are insulating and the bottom is completely
    covered by the sample, which is assumed to be a good
    conductor. The tip of the electrode is a thin insulated wire
    \notaL{El punto del electrodo hazlo más chico que el ancho
      del cable.} with just the tip uncovered and located at $\bm r_0=(x_0,y_0,z_0)$ within the
    liquid.}
  \label{f:celda}
\end{figure}
Within the electrolyte the current density is
\begin{equation}
  \label{eq:j}
  \bm j=\sigma\bm E,
\end{equation}
with
$\sigma$ the conductivity, $\bm E=-\nabla\phi$ the electric field,
and $\phi$ the electric potential. For a
stationary situation\notaL{Latex usa nabla como el nombre de
  $\nabla$}
$\nabla\cdot \bm j = \sigma\nabla\cdot\bm E=0$. Thus, within the electrolyte,
\begin{equation}
  \label{eq:laplace}
\nabla^{2} \phi=0.
\end{equation}
Consider now an arbitrary closed surface
$\mathcal S$
within the electrolyte that surrounds completely the tip of the
electrode. Integrating $ \bm j$ over this surface we obtain
\begin{equation}
  \label{eq:I}
\int_{\mathcal S'} d\bm a \cdot \bm j = -I,
\end{equation}
where the prime on $\mathcal S'$ means we remove from the surface a
very small hole through which the wire that feeds the current to the
electrode gets
through. Assuming the wire is narrower than any other relevant
distance in the system, we may interpret Eq. \eqref{eq:I} as an
integral over a closed surface of the current \eqref{eq:j} within the
electrolyte, ignoring the actual current within the wire. Thus
\begin{equation}
  \label{eq:gauss}
  \int_{\mathcal S} d\bm a \cdot \bm E = -\frac{I}{\sigma}
\end{equation}
Using Gauss's law, we interpret this equation as a source for the
potential in the form of a point charge
\begin{equation}
  q_0 = -\frac{I}{4 \pi \sigma}
\end{equation}
at the position $\bm r_0=(x_0, y_0, z_0)$ of the
tip of the electrode. Note that $q_0$ would be the total charge,
and it shouldn't be further screened through the permittivity of the
electrolyte.

@@

We consider first a system made of identical unit charges
ocuppying the positions $\bm R$ of a 2D Bravais lattice $\{\bm R\}$,
which we will take as a rectangular lattice with lattice parameters
$2a$ and $2b$, and lying, for the time being, at the $z=0$ plane.
The potential it produces obeys
\begin{equation}
  \label{eq:poissonRed}
  \nabla^2\phi(\bm r)=-4\pi\sum_{\bm R}\delta(\bm r_\|-\bm
  R)\delta(z)=-\frac{4\pi}{A}\sum_{\bm G}e^{i\bm G\cdot\bm r_\|}\delta(z),
\end{equation}
where $\bm r_\|$ is the projection of the observation position $\bm
r=(x,y,z)$ onto the $xy$ plane,
$\delta(\ldots)$ is Dirac's delta function, $\{\bm G\}$ is the
reciprocal lattice defined through $e^{i\bm G\cdot\bm R}=1$ for all
$\bm R$ and $\bm G$, $A=4ab$ is the area of the unit cell
and we used the Fourier representation of the 2D
periodically repeated delta function. We introduce a 2D Fourier representation for
the potential \notaL{\sout{Checar consistencia entre phi y varphi en todos lados}}
\begin{equation}
  \label{eq:phifourier}
  \phi(\bm r)=\sum_{\bm G}\phi_{\bm G}(z)e^{i\bm G\cdot\bm r_\|}
\end{equation}
where $\phi_{\bm G}(z)$ is the Fourier coefficient of the potential at
the height $z$. Substitution in Eq. \eqref{eq:poissonRed} yields the
ordinary differential equation \notaL{\sout{El signo estaba mal. Chécalo.}} \notaC{En efecto el sino 
estaba mal yo tenia +, y es - por la ecuacion de segundo orden que sale en este caso, tenia tambien 
derivadas parciales y son totales}
 \begin{eqnarray}
 \frac{d^2}{dz^2}\phi_{\bm G}(z)-G^2\phi_G(z)=
   -\frac{4 \pi}{A} \delta(z),
 \end{eqnarray}
an homogeneous equation for $z\ne0$ which may be trivially
solved. After applying boundary conditions at $z=0$ and regularity
conditions at infinity, we obtain
\begin{equation}
  \label{eq:phiG}
  \phi_{\bm G}(z)=
  \begin{cases}
    -\dfrac{2\pi}{A}\abs{z}&\text{if }G=0,\\
    \dfrac{2 \pi}{AG}  e^{- G \abs{z}}&\text{if }G\neq 0.
  \end{cases}
\end{equation}
The case $G=0$ corresponds to the potential produced by a uniformly charged plane,
while the case $G\ne 0$ is the potential produced by a sinusoidal
charge density on a plane given by the
symmetric solution that decays exponentially as we get away from
the source plane. Substituting into Eq. \eqref{eq:phifourier} yields
\begin{eqnarray}
  \label{eq:phiG1}
 \phi(\bm r) = -\frac{2 \pi}{A}  \abs{z} +{\sum_{\bm G}}' \frac{2 \pi
   }{AG} e^{- G \abs{z}} e^{i \bm G\cdot\bm r_\|},
 \end{eqnarray}
where the prime indicates that the term $G=0$ should be ommited from
the sum.

@@

\notaL{\sout{Cambié el título, pues tienes una mezcla de experimento y
  teoría aquí}}
In Fig. \ref{fig:DE1} we show a schematic representation of our
experimental setup to manufacture porous silicon with GRIN.
\notaL{\sout{Cambié las figuras}}
As dicussed above, we fabricated an electrolytic cell with the shape of a
rectangular prism on the bottom of which we place a Si wafer which makes
electrical contact to a metal plate \notaC{\sout{gold plate} error de escritura} 
\notaL{\sout{Lo inventé; de qué material es el contacto bajo la muestra}}
 which together make the anode. The catode consists of a platinum wire 
 insulated except for a small region at its tip, which we take as a 
 point current drain.
We also show a schematic drawing of the expected GRIN PS structures,
with a gradient in the porosity, and in the thickness, density and depth
of the resulting pores.

\subsection{Fabrication of PS  GRIN Single Layers}
\label{sec:fabrication-ps-grin}
We manufactured single layer PS structures through an electrochemical
anodization on a (100) $p$-type crystalline Si wafer
(resistivity 0.002 - 0.005 $ \Omega\,\text{cm}$), under galvanostatic
conditions. The process was performed at
room temperature,\notaL{OJO. No controlaste la temperatura} with an
electrolytic mixture of aqueous hydrofluoric
acid (HF) (concentration 48\% wt), glycerol (purity 99.8 \% wt) and
ethanol (purity 99.9\% wt) in a 3:7:1 volume ratio. After the
anodizing process, the samples were rinsed with
ethanol (purity: 99.9 $ \% $  wt). The electrolytic cell had the shape
of a rectangular prism as shown in Fig. \ref{fig:DE1}, with a base of
size $0.62\text{cm}\times2.03\text{cm}$) with an uncovered sample area
of $1.206\text{cm}^2$. \notaC{Estan son las coordenadas del electrodo} The coordinates the tip of the
electrode at $\bm
r_0=(x_0,y_0,z_0)=(0.1\text{cm},0.3\text{cm},0.9\text{cm})$
\notaL{\sout{¿Cuáles fueron las coordenadas del
  electrodo?}} We manufactured samples using a current $I=5\text{mA}$
which yielded current densities in the range
$j_\perp=2.5-6.0\text{mA}/\text{cm}^2$ and other samples using a larger
current $I=40\text{mA}$ corresponding to current densities in the
range $j_\perp=20-50\text{mA}/\text{cm}^2$.
\subsection{Morphological studies}
\label{sec:morph-stud}
\notaL{Cambié el orden}
The morphologies of the etched porous layers were
observed using a Hitachi SU1510 scanning electron microscope (SEM)
with which we measured the thickness $d$ and the porosity $p$ of the
films at different positions along the sample from its top and side
views (Fig. \ref{fig:DE1}).

\subsection{Reflectance Measurement}
\label{sec:refl-meas}
We measured the reflectivity spectra using a {\em Perkin Elmer Lambda 950}
UV-Vis-NIR spectrophotometer. For iterpretation of the data in the
case of a single PS layer we used
the standard formula \cite{T8,T9} \notaL{\sout{referencia}} for three media air (0), PS
(1) and c-Si (2),
 \begin{eqnarray}\label{Eq:ECMR}
   R=\frac{r _ {_ {01}}r _ {_ {12}} e^{2i\delta}}{1+r _ {_ {01}}r _ {_ {12}} e^{2i\delta}}
\end{eqnarray}
where $ r_{01} $ y $ r_{12}$ are the Fresnel reflectance
coefficients at the air/PS and PS/c-Si interfaces \cite{T10,T11}\notaL{\sout{referencias}}
and $\delta=k_{PS}^\perp d$, where $k_{PS}^\perp$ is
the component of the wavevector perpendicular to the surface within
the porous layer of thickness $d$.
\notaL{Me tienes que explicar dónde y cómo usaste lo que mencionas en
  la siguiente frase:
The advantage of this method is
the possibility of taking into account the interface roughness effect
by including the Davies-Bennett factor in the coefficient of each
Fresnel cite{I17, I18, I19}, which represents the roughness of a
Gaussian distribution.}} \notaC{No tenia ninguna relevancia en este 
punto de la discusión, y si fue una equivocación dejarla hasta el 
final}

\subsection{Refraction Index of PS GRIN Single Layers}
\label{sec:refraction-index-ps}
The local refractive index $n_{PS}$ of the PS layer was calculated from its
porosity $p$ through
Bruggeman's effective medium theory \cite{I20} \notaL{Elegir y checar:
  $\varepsilon o \epsilon$ para funciones dieléctricas}
\begin{eqnarray}\label{Eq:Brugg}
 p\frac{1-\varepsilon_{PS}} {1+\varepsilon_{PS}} + (1-p)
  \frac{\varepsilon_{\text{Si}} - \varepsilon_{PS}}
  {\varepsilon_{\text{Si}}+\varepsilon_{PS}}=0
\end{eqnarray}
\notaL{Te faltaba la igualdad}
where the porosity $p$ is the volume fraction of air within the PS
layer, $\varepsilon_{Si}$ is the dielectric function of c-Si, and
$\varepsilon_{PS}=n_{PS}^2$ is the dielectric function of the PS.
\notaL{Quité frases irrelevantes.}
\subsection{Fabrication  of GRIN PS Microcavities}
\label{sec:fabrication-grin-ps}
After characterizing the fabrication process through measurements and
calculations corresponding to single PS GRIN layers, we
fabricated PS GRIN microcavities (MC) as specific defects between two distributed Bragg
mirrors  (DBR). Alternate quarter wavelength plates of high (H) and low (L)
refractive indices $n_i$ of thickness $d_i$, $i=H,L$ were prepared satisfying the Bragg condition
$n_id_i=\lambda_c/4$ at a given design
wavelength $\lambda_c$ and at a position $A$ (Fig. \ref{fig:DE1}) which
we chose as that directly below the point-like electrode.\notaL{Checar
  veracidad} The defect
was chosen as a half-wavelength high index layer of thickness $d_d=2d_H$ such that
$n_Hd_h=\lambda_c/2$. The MC corresponds to the
sequence $(HL)_6HH(LH )_6$ where each letter $H$ or $L$ corresponds to
a quarter wavelength plate of high and low index of refraction correspondingly.
We chose $\lambda_c= 0.67 \mu\text{m}$.\notaL{Algún motivo para esta
  elección?} For preparing the high index layers we
chose a current $I_H=5\text{mA}$ which corresponded to a current density
$j_{HA\perp}= 6\text{mA}/\text{cm}^2$ below the tip \notaL{checar}, and yielded
$n_H =2.6$, corresponding to a porosity \notaL{Explicar esta
  correspondencia entre $p$ y $n$} \notaL{P mayúscula
  es porosidad, o p minúscula. Checar consistencia} $p_H =0.46$, and a
thickness $d_H=0.066 \mu\text{m}$, which required an attack time of
$t_H=35 \text{s}$. The corresponding parameters for the low density
layers were $I_L=38\text{mA}$, $j_{LA\perp}=50\text{mA}/\text{cm}^2$, $n_L= 1.4$,  $p_L =0.75$,
$d_L=0.117 \mu \text{m}$, and $t_L=11 \text{s}$. For the rest of the
sample the current density, porosity, index of refraction and thickness
varied, yielding a GRIN MC.

@@

\subsection{PS GRIN Single Layer }
\label{sec:ps-grin-single}
\notaL{Quité la figura pues no añade nada}
\notaL{Quité la descripción, pues está arriba}
  \includegraphics[width=\textwidth]{Images/SPgrin51}
  \caption{(a)  Sample $G_1$ prepared as described in
     \ref{sec:fabrication-ps-grin} using a current $I_1=5 \text{mA}$
    during a time $t_1=600\text{s}$. We indicate three regions $A$,
    $B$, and $C$ centered at positions at positions,
    $x_A=0.3\text{cm}$ \notaL{Atrás habías dicho que era justo abajo
      del electrodo. ¿Es cierto o no? ¿Dónde estaba el electrodo? ¿Qué
    altura tenía el agua? ¿Igual que en la sección previa?}, $x_B=0.8\text{cm}$ and
    $x_C=1.7\text{cm}$. \notaL{¿Cuánto vale $y$?} (b) Reflectance
    spectra measured at the center of regions $A$, $B$, and $C$ and fit
    using Eq. \eqref{Eq:ECMR}.\notaL{¿Cuáles parámetros se ajustaron y
      cuáles se midieron independientemente}\notaL{Para que no se vean
      tan chicas las figuras, quita las R's y los números en el segundo
      renglon, excepto en el extremo izquierdo, y pega las tres
      figuras una tras la otra. Haz lo mismo en el tercer renglón,
      quitando dos de los letreros Refractive index, pero antes
      asegúrate de usar la misma escala en las tres figuras} (c)
    Corresponding complex indices of refraction $n+ik$ obtained from
    Eq. \eqref{Eq:Brugg} using the fitted porosities $p_{1A}=0.44$,
    $p_{1B}=0.42$, and $p_{1C}= 0.40$ at the chosen positions. \notaL{En las
      figuras escribe A, B y C en lugar de
      Point A, Point B y Point C. Escribe $p_{1A}$, $p_{1B}$ y $p_{1C}$ en lugar
      de la palabra Porosity. Escribe $n$ y $k$ nada más, sin la
      palabra Real ni Imaginary. Usa Theory en lugar de
      Simulation. Usa línea a trazos para la parte
      imaginaria. Alínea todos los letreros. En inglés, los rótulos
      a), b) y c) se escriben como (a), (b) y (c), aunque creo que se
      pueden eliminar (porque además, no los alineaste bien). }
  \notaL{A ojo no se notan las diferencias en epsilon. Mejor junta las
  tres partes reales en una sola gráfica y las tres partes imaginarias
en otra y ponerlas una al lado de la otra.}\notaL{Las letras A, B y C
están colocadas en el lugar preciso, a escala?}\notaL{Quizás sea mejor
que hagas tres figuras distintas, una para cada panel, y las alineamos
con latex}}
  \label{fig:DR3}
 In Fig. \ref{fig:DR3} we show a photograph of one of our single layer PS GRIN
 structures, $G_1$, prepared as described in
 \ref{sec:fabrication-ps-grin} applying a current $I_1=5\text{mA}$ for
 $t_1=600\text{s}$.\notaL{Quizás podamos quitar la repetición de I y
   t} We employed the same geometry as that described in
 Sec. \ref{sec:current-density} \notaL{Lo inventé. ¿Es cierto?}
The position of electrode corresponds to the upper left side of the
photograph. The variation of the optical properties across the
sample is evident. We chose three positions $x_A=0.3\text{cm}$,
$x_B=0.8\text{cm}$ and $x_C=1.7\text{cm}$ \notaL{¿Son correctos estos
  valores? Antes dijiste que $A$ estaba abajo del electrodo}\notaL{¿valor de y?} on
which we measured the reflectance spectra, also shown in the figure.
We fitted the measurements using Eqs. \eqref{Eq:ECMR} and
\eqref{Eq:Brugg} using the local porosity and the depth of the layer
as adjustable parameters. \notal{¿Es cierto?} We obtained $p_{1A}=0.44$, $p_{1B}=0.42$, and
$p_{1C}= 0.40$. \notaL{Falta decir cuáles fueron las profundidades}
Location $A$ is
closest to the electrode, while location $C$ is the furthest.
\notaL{Quité una frase sin sentido.}
We also show in Fig. \ref{fig:DR3} the wavelength dependence of
 the complex index of refraction corresponding to the fitted porosities.
\notaL{\sout{Quité otra frase que no entendí, pero que me generó una duda:
  la profundidad la ajustaste ópticamente o la mediste en SEM y luego
  hiciste el ajuste a la reflectancia?}} \notaC{Esta parte, siempre se midio la
  profundida en SEM, por eso me costo poder ajustar el espectro de reflactacia
  en un primer inicio, hasta que coloque la ecuacion de de fresnel
  para una monopelicula.}

@@

 \bibitem{T8}Born, Max, and Emil Wolf. \textquotedblleft \emph{Basic properties of 
   	the electromagnetic field.}\textquotedblright Principles of optics 44 (1980).
  \bibitem{T9} Stenzel, Olaf. \textquotedblleft \emph{ The physics of thin film 
  	optical spectra.}\textquotedblright Springer, 2015.

  \bibitem{T10}Born, Max, and Emil Wolf.\textquotedblleft \emph{ Principles of optics: 
  	electromagnetic theory of propagation, interference
  	 and diffraction of light.}\textquotedblright Elsevier, 2013.
  \bibitem{T11} Sattler, Klaus D., ed. \textquotedblleft \emph{ Silicon Nanomaterials 
  	Sourcebook: Low-Dimensional Structures, Quantum Dots, and Nanowires }\textquotedblright,
   Volume One. CRC Press, 2017.
